An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-05-20 Revision/R1_latex/manuscript.tex
Convert eps figures to pdf

\begin{figure}[h!]
	\center
	\subfloat[\label{}]{%
	\includegraphics[scale=2.0]{local_search_definitions_flower.png}
	}\hspace{40pt}%
	\subfloat[\label{}]{%	
	\includegraphics[scale=0.3]{local_search_definitions_cellular-grid-illustration.eps}
	}
	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region. In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
	\label{fig:cellular-grid-model}
\end{figure}

@@

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.03]{local_search_definitions_R3.eps}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{local_search_definitions_glued-curve.eps}
	}%	
	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
\end{figure}

@@

\begin{figure}[!h]
	\center
	\begin{tabular}{ccc}
		$h=1.0$ & $h=0.5$ & $h=0.25$\\
		\includegraphics[scale=0.2]{local_search_square_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h025_summary.eps} \\
		\includegraphics[scale=0.2]{local_search_flower_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h025_summary.eps}
	\end{tabular}	
		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $5$ for the square and flower shapes. Shapes are displayed at every $5$ iterations.}}	
		\label{fig:local-comb-square-results}		
\end{figure}

@@

\begin{figure}[!h]
\center
\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_square.eps}}
\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_flower.eps}}
\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value close to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
\label{fig:plot-elastica-local-search}
\end{figure}

@@

\begin{figure}
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{flow_contour-information_before-opt.eps}
\label{fig:contour-info-1}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{flow_contour-information_after-opt.eps}
\label{fig:contour-info-2}
\end{minipage}%
\caption{ \revision{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}}
\label{fig:contour-info}
\end{figure}

@@

\begin{figure}[!h]
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-nolength_summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-length015_summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r5_summary_flow.eps}
	}%
\end{minipage}%
\caption{The algorithm is very sensitive to the little variations of the estimator, which are particularly important in regions of low squared curvature. Artifacts are somewhat reduced with a length penalization but increases if we use a higher ball radius. }
\label{fig:m1-square-flow}
\end{figure}

@@

\begin{figure}[!h]
\center
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=1$\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l1_summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=3$\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l3_summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[\revision{$r=5, m=5$}\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l5_summary_flow.eps}
	}%
\end{minipage}%
\caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
\end{figure}

@@

\begin{figure}[hp!]
\center				
		\setcounter{subfigure}{-3}
		\subfloat[$r=3,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r3-h05_summary_flow.eps}
		}%
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r3-h05_summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r3-h05_summary_flow.eps}}%
		}

		\setcounter{subfigure}{-2}
		\subfloat[$r=5,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r5-h05_summary_flow.eps}
		}%1
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r5-h05_summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r5-h05_summary_flow.eps}}%
		}\\
		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
		\includegraphics[scale=0.5]{flow_elastica-energy-plot_square-flower-triangle.eps}						
		}
\caption{The choice of radius impacts the flow. In the figures, the flow ceases to evolve for all shapes  when $r=3$ (a). In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a). In figure (c), we observe that for a given choice of radius, the digital elastica may increase after a certain number of iterations. }
\label{fig:mx-flow-gs-radius-effect}
\end{figure}

\begin{figure}[!h]
\center
\subfloat[]{%
	\includegraphics[scale=0.5]{flow_faster-high-curvature_summary_flow.eps}}\\%
\subfloat[]{%
		\includegraphics[scale=0.25]{flow_fill-holes_summary_flow.eps}}%%1
\caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
\label{fig:mx-speed-variation-hole-filling}
\end{figure}

@@

\begin{figure}
\center
\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.eps}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
\label{fig:ratio-pairwise-terms}
\end{figure}

\begin{figure}[]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for varying radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

>>>>

\begin{figure}[h!]
	\center
	\subfloat[\label{}]{%
	\includegraphics[scale=2.0]{local_search_definitions_flower.png}
	}\hspace{40pt}%
	\subfloat[\label{}]{%	
	\includegraphics[scale=0.3]{local_search_definitions_cellular-grid-illustration.pdf}
	}
	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region. In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
	\label{fig:cellular-grid-model}
\end{figure}

@@

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.03]{local_search_definitions_R3.pdf}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{local_search_definitions_glued-curve.pdf}
	}%	
	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
\end{figure}

@@

\begin{figure}[!h]
	\center
	\begin{tabular}{ccc}
		$h=1.0$ & $h=0.5$ & $h=0.25$\\
		\includegraphics[scale=0.2]{local_search_square_h1_summary.pdf} & \includegraphics[scale=0.2]{local_search_square_h05_summary.pdf} & \includegraphics[scale=0.2]{local_search_square_h025_summary.pdf} \\
		\includegraphics[scale=0.2]{local_search_flower_h1_summary.pdf} & \includegraphics[scale=0.2]{local_search_flower_h05_summary.pdf} & \includegraphics[scale=0.2]{local_search_flower_h025_summary.pdf}
	\end{tabular}	
		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $5$ for the square and flower shapes. Shapes are displayed at every $5$ iterations.}}	
		\label{fig:local-comb-square-results}		
\end{figure}

@@

\begin{figure}[!h]
\center
\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_square.pdf}}
\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_flower.pdf}}
\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value close to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
\label{fig:plot-elastica-local-search}
\end{figure}

@@

\begin{figure}
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{flow_contour-information_before-opt.pdf}
\label{fig:contour-info-1}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{flow_contour-information_after-opt.pdf}
\label{fig:contour-info-2}
\end{minipage}%
\caption{ \revision{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}}
\label{fig:contour-info}
\end{figure}

@@

\begin{figure}[!h]
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-nolength_summary_flow.pdf}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-length015_summary_flow.pdf}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r5_summary_flow.pdf}
	}%
\end{minipage}%
\caption{The algorithm is very sensitive to the little variations of the estimator, which are particularly important in regions of low squared curvature. Artifacts are somewhat reduced with a length penalization but increases if we use a higher ball radius. }
\label{fig:m1-square-flow}
\end{figure}

@@

\begin{figure}[!h]
\center
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=1$\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l1_summary_flow.pdf}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=3$\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l3_summary_flow.pdf}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[\revision{$r=5, m=5$}\label{}]{%
	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l5_summary_flow.pdf}
	}%
\end{minipage}%
\caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
\end{figure}

@@

\begin{figure}[hp!]
\center				
		\setcounter{subfigure}{-3}
		\subfloat[$r=3,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r3-h05_summary_flow.pdf}
		}%
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r3-h05_summary_flow.pdf}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r3-h05_summary_flow.pdf}}%
		}

		\setcounter{subfigure}{-2}
		\subfloat[$r=5,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r5-h05_summary_flow.pdf}
		}%1
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r5-h05_summary_flow.pdf}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r5-h05_summary_flow.pdf}}%
		}\\
		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
		\includegraphics[scale=0.5]{flow_elastica-energy-plot_square-flower-triangle.pdf}						
		}
\caption{The choice of radius impacts the flow. In the figures, the flow ceases to evolve for all shapes  when $r=3$ (a). In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a). In figure (c), we observe that for a given choice of radius, the digital elastica may increase after a certain number of iterations. }
\label{fig:mx-flow-gs-radius-effect}
\end{figure}

\begin{figure}[!h]
\center
\subfloat[]{%
	\includegraphics[scale=0.5]{flow_faster-high-curvature_summary_flow.pdf}}\\%
\subfloat[]{%
		\includegraphics[scale=0.25]{flow_fill-holes_summary_flow.pdf}}%%1
\caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
\label{fig:mx-speed-variation-hole-filling}
\end{figure}

@@

\begin{figure}
\center
\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.pdf}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
\label{fig:ratio-pairwise-terms}
\end{figure}

\begin{figure}[]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.pdf}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.pdf}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for varying radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}
